Inference methods comparison for the simplified Naomi model

### 2023-02-07 src/naomi-simple_compare/comparison.Rmd
Add histograms and ECDF for all latent field elements too

>>>>

## `u_rho_x`

```{r}
histogram_and_ecdf_helper <- function(par) lapply(1:sum(names(tmb$fit$obj$env$par) == par), histogram_and_ecdf, par = par)
histogram_and_ecdf_helper("u_rho_x")
```

## `u_rho_x`

```{r}
histogram_and_ecdf_helper("u_rho_x")
```

## `us_rho_x`

```{r}
histogram_and_ecdf_helper("us_rho_x")
```

## `u_rho_xs`

```{r}
histogram_and_ecdf_helper("u_rho_xs")
```

## `us_rho_xs`

```{r}
histogram_and_ecdf_helper("us_rho_xs")
```

## `u_rho_as`

```{r}
histogram_and_ecdf_helper("u_rho_as")
```

## `u_alpha_x`

```{r}
histogram_and_ecdf_helper("u_alpha_x")
```

## `us_alpha_x`

```{r}
histogram_and_ecdf_helper("us_alpha_x")
```

## `u_alpha_xs`

```{r}
histogram_and_ecdf_helper("u_alpha_xs")
```

## `us_alpha_xs`

```{r}
histogram_and_ecdf_helper("us_alpha_xs")
```

## `u_alpha_a`

```{r}
histogram_and_ecdf_helper("u_alpha_a")
```

## `u_alpha_as`

```{r}
histogram_and_ecdf_helper("u_alpha_as")
```

## `u_alpha_xa`

```{r}
histogram_and_ecdf_helper("u_alpha_xa")
```

## `ui_lambda_x`

```{r}
histogram_and_ecdf_helper("ui_lambda_x")
```

## `ui_anc_rho_x`

```{r}
histogram_and_ecdf_helper("ui_anc_rho_x")
```

## `ui_anc_alpha_x`

```{r}
histogram_and_ecdf_helper("ui_anc_alpha_x")
```

## `log_or_gamma`

```{r}
histogram_and_ecdf_helper("log_or_gamma")
```
